---
title: 'Lab 2: Data Visulization'
date: "September 28, 2020"
output:
  html_document:
    df_print: paged
---
```{r setup, message = F, include=FALSE}
library(tidyverse)
```

Today's agenda: data visualization with tennis grand slams data set. Play with the following R code to figure out what we are doing here.
```{r}
# load data
grand_slams <- read.csv("data/grand_slams.csv")
```
### First plot
Create a scatter plot with rolling_win_count versus tournament_date. Explain what you see in the plot.
```{r}
library(ggplot2)
```
```{r}
ggplot(data = grand_slams) +
  geom_point(aes(x = tournament_date, y = rolling_win_count))
```

### Second plot
Now,  cut down the data, plot data again with player names as colour.

```{r}
ggplot(data = grand_slams) +
  geom_point(aes(x = tournament_date, y = rolling_win_count, color = name))
```

```{r}
more_than_10_wins <- grand_slams %>%
      group_by(name) %>%
      filter(any(rolling_win_count > 10))

ggplot(data = more_than_10_wins) +
  geom_point(aes(x = tournament_date, y = rolling_win_count, color = name))
```

```{r}

```

### Third plot
Simple bar plot. 
```{r}
ggplot(data = more_than_10_wins, aes(x = name)) +
geom_bar()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Now change bar color with `fill`.
```{r}
ggplot(data = more_than_10_wins, aes(x = name, fill = grand_slam)) +
geom_bar()+
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```


### Fourth plot
Days from first win.
```{r}
more_than_10_wins <- more_than_10_wins %>% group_by(name) %>%
mutate(
first_win = min(tournament_date), days_since_first = as.numeric(tournament_date - first_win))
```
Plot lines grouped by player and split by gender.
```{r}
ggplot(data= more_than_10_wins, mapping = aes(
  x = days_since_first,
  y = rolling_win_count,
  
))
```


